---
title: "Review of downy mildew models in grape vines"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DownyMildewReview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Install libraries  

```{r setup}
library(data.table)
library(viticolR)
# if epiphytoolR is not installed, install the 'dev' version from github
if(isFALSE("epiphytoolR" %in% installed.packages()[,"Package"])){
  devtools::install_github("https://github.com/PaulMelloy/epiphytoolR",ref = "dev")
}
library(epiphytoolR)
library(ggplot2)
```

## Define Treatments  
Lets define the field spatially and the treatments we are applying.  

### Vine varieties  
There are four varieties of grapes, roughly evenly split over the vineyard.  
  - Montepulciano (11 rows)  
  - Saperavi (13 rows)  
  - Petit Manseng (23 rows)  
  - Fiano (13 rows)  

Each row is approximately 70 meters long.

### Fungicide treatments  
  - **high** Fungicide frequency  
  - **model** Fungicide application as per the model  
  - **control** Negative control with no application  

### Other considerations  
  - **Fungicide type** will be threshold based, commencing with a rotation of 
  a plant defence regulator (Serenade) and organic protectants (bicarb), increasing 
  to protectants and synthetic fungicides depending on disease severity.  
  - **Replicates** Four  
  - **plot width** Three rows wide  
  - **plot length** 10 meters long  
  
### Obtain spatial map of treatments

```{r define_map}
# Wine varieties
varieties <- 4
## Treatments
treat_n <- 3
# Replicates
reps <- 4 
# total plots
total_p <- varieties * treat_n * reps

# randomised split block plot 
plots_per_range <- treat_n
plots_per_row <- reps

# randomised_split_plot <-
#   rbindlist(# variety one
#     list(
#     data.table(
#        treat = as.vector(replicate(reps,sample(1:treat_n))), # randomise each block
#        plot = rep(seq(from = 1,to = total_p, by = plots_per_row),reps), # find the plot numbers in the first range
#            # replicate plot numbers for each range
#           #(rep((1:plots_per_row)-1, each=plots_per_range)) # add to each range to move 
#        variety = rep("Montepulciano",12)
#     ),
#     data.table(
#        treat = as.vector(replicate(reps,sample(1:treat_n))), # randomise each block
#        #plot = seq(from = 1,to = total_p, by = plots_per_row), # find the plot numbers in the first range
#            # replicate plot numbers for each range
#           #(rep((1:plots_per_row)-1, each=plots_per_range)) # add to each range to move 
#        variety = "Saperavi"
#     ),
#     data.table(
#        treat = as.vector(replicate(reps,sample(1:treat_n))), # randomise each block
#        #plot = seq(from = 1,to = total_p, by = plots_per_row), # find the plot numbers in the first range
#            # replicate plot numbers for each range
#           #(rep((1:plots_per_row)-1, each=plots_per_range)) # add to each range to move 
#        variety = "Petit Manseng"
#     ),
#     data.table(
#        treat = as.vector(replicate(reps,sample(1:treat_n))), # randomise each block
#        #plot = seq(from = 1,to = total_p, by = plots_per_row), # find the plot numbers in the first range
#            # replicate plot numbers for each range
#           #(rep((1:plots_per_row)-1, each=plots_per_range)) # add to each range to move 
#        variety = "Fiano"
#     ))
#   )     
# randomised_split_plot
```  

Here is our treatment list

```{r}
# field_plan <- 
#   create_inf_xyz(plot_length = 10,
#                plot_width = 1,
#                paddock_length = 70,
#                paddock_width = (3 * (12+13+23+13) + 10),# number of rows of each variety +10m for outside buffer
#                infected_plots = total_p,
#                n_plots =  total_p,
#                external_buffer_end = 2,
#                external_buffer_adj = 5,
#                internal_buffer_adj = 2,
#                internal_buffer_end = 5,
#                verbose = TRUE)
# 
# head(field_plan)
```
Let's plot this to see if it is suitable  

```{r}
# field_plan |>
#   ggplot(aes(x=x,y=y,z=load))+
#   geom_raster()
```



```{r}
# merge_axf_weather(File_compressed = paste0("~/weather_data/tgz/240915_0946_IDQ60910.tgz"),
#                   File_axf = "IDQ60910.99123.axf",
#                   File_formatted = "23-24_NTamborine.csv",
#                   base_dir = weather_path,verbose = TRUE
# )
# 
# class(ntw$aifstime_utc)
# ntw[,aifstime_utc := as.character(aifstime_utc)]
# ntw[,aifstime_local := as.character(aifstime_local)]
# 
# fwrite(ntw, "/home/pmelloy/weather_data/23-24_NTamborine.csv")
# fread("/home/pmelloy/weather_data/23-24_NTamborine.csv",integer64 = "character")

```

